Spatial and Temporal Analysis of Bicycle Thefts in Toronto

### 2024-11-08 paper/A2-starter-code.Rmd
paper setups

---
title: "A2 Sample"
author: "Author A & Author B"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)
required_packages <- c("lubridate", "sf", "tidyverse")
for (p in required_packages) {
  if (!require(p, character.only = TRUE)) {
    install.packages(p, character.only = TRUE)
  }
}
library(tidyverse)
library(sf)
# you are welcome to use either the CSV file or the GeoJSON file
# GeoJSON format maybe useful if you would like to combine
# an external geospatial dataset
bike_thefts_csv <- read_csv("data/Bicycle_Thefts_Open_Data.csv") |>
  mutate(
    occurence_date = as_date(
      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    ),
    report_date = as_date(
      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    )
  )
bike_thefts_sf <- read_sf("data/Bicycle_Thefts_Open_Data.geojson") |>
  mutate(
    occurence_date = as_date(
      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    ),
    report_date = as_date(
      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    )
  )
```

>>>>

---
title: "Spatial and Temporal Analysis of Bicycle Thefts in Toronto"
subtitle: "Trends, Patterns, and Insights"
author: "Yingke He, Ziheng Zhong"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include=TRUE, eval=TRUE)
required_packages <- c("lubridate", "sf", "tidyverse", "readr", "here")
for (p in required_packages) {
  if (!require(p, character.only = TRUE)) {
    install.packages(p, character.only = TRUE)
  }
}

library(tidyverse)
library(sf)
library(readr)
library(here)

# you are welcome to use either the CSV file or the GeoJSON file
# GeoJSON format maybe useful if you would like to combine
# an external geospatial dataset
bike_thefts_csv <- read_csv(here("data/Bicycle_Thefts_Open_Data.csv")) |>
  mutate(
    occurence_date = as_date(
      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    ),
    report_date = as_date(
      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    )
  )
bike_thefts_sf <- read_sf(here("data/Bicycle_Thefts_Open_Data.geojson")) |>
  mutate(
    occurence_date = as_date(
      OCC_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    ),
    report_date = as_date(
      REPORT_DATE, format = "%a, %d %b %Y %H:%M:%S GMT"
    )
  )
```
